---
title: "Taren Sanders"
pagetitle: "Taren Sanders"
toc: false
page-layout: full
listing:
  - id: recent-pubs
    contents: _data/publications.json
    type: default
    template: assets/pub-card.ejs
    max-items: 5
    sort: ["date desc"]
    fields: [title, author, journal, year, doi, cites, impact_factor, abstract, wos_id, scopus_id, scholar_id]
  - id: recent-posts
    contents: "blog/*/index.qmd"
    type: default
    max-items: 3
    sort: ["date desc"]
    fields: [date, title, description, reading-time]
---

```{r setup}
#| include: false
profile <- jsonlite::read_json("_data/profile.json")
# Declare dependencies so tar_quarto re-renders when these change.
invisible(try(targets::tar_read(site_profile_json), silent = TRUE))
invisible(try(targets::tar_read(site_pubs_json), silent = TRUE))
```

::: {.hero}
![](assets/profile.svg){.avatar fig-alt="Photo of Taren Sanders"}

::: {.hero-text}
# Taren Sanders

::: {.tagline}
Associate Professor at the Institute for Positive Psychology and Education,
Australian Catholic University. I research physical activity, sleep, and
wellbeing across the lifespan, with a focus on rigorous methods and open
science.
:::
:::
:::

::: {.badges}
[![ORCID](https://img.shields.io/badge/ORCID-0000--0002--4504--6008-A6CE39?logo=orcid&logoColor=white)](https://orcid.org/0000-0002-4504-6008)
[![Google Scholar](https://img.shields.io/badge/Scholar-Profile-4285F4?logo=googlescholar&logoColor=white)](https://scholar.google.com/citations?user=8KNzhS4AAAAJ)
[![GitHub](https://img.shields.io/badge/GitHub-tarensanders-181717?logo=github)](https://github.com/tarensanders)
[![ACU](https://img.shields.io/badge/Affiliation-ACU%20IPPE-660066)](https://www.acu.edu.au/research/our-research-institutes/institute-for-positive-psychology-and-education)
:::

```{r metrics, echo=FALSE, results='asis'}
fmt <- function(x) if (is.null(x) || is.na(x)) "—" else format(x, big.mark = ",")
cat(sprintf(
'<div class="metrics">
  <div class="metric"><span class="value">%s</span><span class="label">Citations</span></div>
  <div class="metric"><span class="value">%s</span><span class="label">h-index</span></div>
  <div class="metric"><span class="value">%s</span><span class="label">i10-index</span></div>
  <div class="metric"><span class="value">%s</span><span class="label">Publications</span></div>
</div>',
fmt(profile$cites), fmt(profile$h_index), fmt(profile$i10_index), fmt(profile$pubs)
))
```

::: {.text-muted style="font-size: 0.85rem;"}
Metrics updated `r profile$updated`.
:::

## Recent publications

::: {#recent-pubs}
:::

[See all publications →](publications.qmd)

## Recent writing

::: {#recent-posts}
:::

[All posts →](blog/index.qmd)
