---
name: Taren Sanders
position: Researcher & Data Scientist
address: "Institute for Positive Psychology and Education, Australian Catholic University"
phone: 0412 278 640
#www: 
email: Taren.Sanders@acu.edu.au
twitter: tarensanders
github: tarensanders
orcid: "0000-0002-4504-6008"
aboutme: ""
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: "000000"
csl: "apa-cv.csl"
params:
  long: true
output: 
  vitae::awesomecv:
    pandoc_args: ["--lua-filter=strong.lua"] 
    keep_tex: false
    includes:
      in_header: header.tex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
# target knits Rmds in their own session, so load libraries here.
# source(here::here("packages.R")) # nolint
# if you want access to the functions you've written
# lapply(list.files(here::here("./R"), full.names = TRUE), source) # nolint
```

```{r load-targets, include=FALSE}
tar_load(c(
  funding, students, awards, book_chapters,
  conferences, peer_reviewed_citations,
  research_profile, invited_talks, service,
  development, software
))
```

# Education

```{r education}
tribble(
  # nolint start
  ~Degree, ~University, ~Date, ~Details,
  "Doctor of Philosophy", "Western Sydney University", 2016,
  "Thesis title: Investigating Associations Between Neighbourhood Green Space and Weight Status: A Longitudinal Study of Australian Children Aged 4 to 13 Years Old.",
  "Bachelor of Health Science (Honours; First Class)", "Western Sydney University", 2012,
  "Thesis title: Measuring adolescent boys’ physical activity: Bout length and the influence of accelerometer epoch length.",
  "Bachelor of Health Science (PDHPE)", "Western Sydney University", 2011, NA
  # nolint end
) %>%
  detailed_entries(
    what = University,
    when = Date,
    with = Degree,
    why = Details,
    .protect = FALSE
  )
```

# Employment History

```{r employment}
employment <-
  tribble(
    ~role, ~start, ~end, ~org, ~details,
    # nolint start
    "Program Leader", "2021", "Current",
    "Institute for Positive Psychology and Education, Australian Catholic University",
    list(
      "Drive the strategic direction and focus of the research program",
      "Support academic and professional staff, as well as higher-degree students, within the program",
      "Provide input as a member of the Institute Executive Management Committee on the priorities of the institute, and advocate for my research program",
      "Developed and implemented new project management processes within the program, including making agile management strategies standard practice."
    ),
    "Deputy Program Leader", "2017", "2021",
    "Institute for Positive Psychology and Education, Australian Catholic University",
    list(
      "Supported Program Leader to manage the research program"
    ),
    "Research Fellow", "2016", "Current",
    "Institute for Positive Psychology and Education, Australian Catholic University",
    list(
      "Conduct original, high-impact, and translational research in the areas of health, education, and psychology.",
      "Overseen the development and evaluation of multiple large-scale school-based research projects, including iPLAY (145 schools) and Transform-Us! (20 schools in NSW). Intervention content I created has been delivered to more than 2,500 teachers and impacted more than 40,000 students.",
      "Conducted analyses of primary and secondary data, and provided statistical support to colleagues including statistics workshops.",
      "Worked with industry partners (NSW Department of Education, NSW Health, Sport Australia) to provide project updates and seek input.",
      "Author and co-author academic outputs, including book chapters, journal articles, and grant applications, as well as non-academic outputs such as stakeholder reports and data visualisations.",
      "Mentor doctoral and honours students, including reviewing and evaluating their analyses and writing."
    )
    # nolint end
  )

detailed_entries(
  employment,
  what = org,
  when = glue("{start}--{end}"),
  with = role,
  why = details
)
```

# Research Summary

```{r}
tribble(
  # nolint start
  ~Publications, ~Citations, ~"h-Index", ~"Mean CNCI", ~"Mean Impact Factor", ~Funding,
  research_profile$pubs, research_profile$cites, research_profile$h_index, research_profile$mean_cnci, research_profile$mean_jif, "> $1 million"
  # nolint end
) %>%
  knitr::kable(format = "latex", align = rep("c", 5)) %>%
  kableExtra::row_spec(0, bold = TRUE) %>%
  kableExtra::kable_minimal(latex_options = "hold_position", full_width = TRUE)
```

# Technical Skills

```{r}
tribble(
  ~Category, ~Skill,
  # nolint start
  "Programming Languages", "R, Python, Stata, Julia",
  "Software Development", "R packages (including CRAN submission), Python packages",
  "Statistical Methods", "Machine learning (incl. computer vision), multilevel modelling, intervention evaluation, growth curve modelling",
  "Research Methods", "Study design, intervention development, ethics and recruitment"
  # nolint end
) %>%
  detailed_entries(
    with = Category,
    what = Skill
  )
```

\newpage

`r if (params$long) {"# Publications"} else {"# Selected Publications"}`

`r if (!params$long) {"For a full list of publications see my full CV ([bit.ly/SandersCV](https://bit.ly/SandersCV))."}`

## Peer-Reviewed Publications

`r if (params$long) {"*Note*: In health and medicine the last author is considered the 'senior' author.\nCitations from Web of Science; JIF = [Journal Impact Factor](http://help.prod-incites.com/inCites2Live/indicatorsGroup/aboutHandbook/usingCitationIndicatorsWisely/jif.html); CNCI = [Category Normalised Citation Index](http://help.prod-incites.com/inCites2Live/indicatorsGroup/aboutHandbook/usingCitationIndicatorsWisely/normalizedCitationImpact.html)."}`

```{r publications}
peer_reviewed_citations %>%
  dplyr::filter(if (!params$long) short_cv else TRUE) %>%
  arrange(desc(issued))
```

## Book Chapters

```{r bookchapters}
book_chapters %>%
  arrange(desc(issued))
```

```{r long-sections, child=if(params$long) 'cv/long_sections.Rmd'}
```
