---
name: Taren Sanders
position: Academic Researcher & Data Scientist
address: "Institute for Positive Psychology and Education, Australian Catholic University"
phone: 0412 278 640
#www: 
email: Taren.Sanders@acu.edu.au
twitter: tarensanders
github: tarensanders
orcid: "0000-0002-4504-6008"
aboutme: ""
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: "000000"
csl: "apa-cv.csl"
params:
  two_page: false
  five_page: false
output: 
  vitae::awesomecv:
    pandoc_args: ["--lua-filter=strong.lua"] 
    keep_tex: false
    includes:
      in_header: header.tex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
# target knits Rmds in their own session, so load libraries here.
# source(here::here("packages.R")) # nolint
# if you want access to the functions you've written
# lapply(list.files(here::here("./R"), full.names = TRUE), source) # nolint
```

```{r load-targets, include=FALSE}
tar_load(c(
  funding, students, awards, book_chapters,
  conferences, peer_reviewed_citations,
  research_profile, invited_talks, service,
  development, software
))
```

# Education

```{r education}
tribble(
  # nolint start
  ~Degree, ~University, ~Date, ~Details,
  "Doctor of Philosophy", "Western Sydney University", 2016,
  "Thesis: Investigating associations between neighbourhood green space and weight status: A longitudinal study of Australian children aged 4 to 13 years old.",
  "Master of Data Science (Applied)", "Adelaide University", 2022, NA,
  "Bachelor of Health Science (Honours; First Class)", "Western Sydney University", 2012,
  "Thesis: Measuring adolescent boys’ physical activity: Bout length and the influence of accelerometer epoch length.",
  "Bachelor of Health Science (PDHPE)", "Western Sydney University", 2011, NA
  # nolint end
) %>%
  detailed_entries(
    what = University,
    when = Date,
    with = Degree,
    why = Details,
    .protect = FALSE
  )
```

# Employment History

```{r employment}
employment <-
  tribble(
    ~role, ~start, ~end, ~org, ~details,
    # nolint start
    "Program Leader", "2021", "Current",
    "Institute for Positive Psychology and Education, Australian Catholic University",
    list(
      "Drive the strategic direction and focus of the research program",
      "Support academic and professional staff, as well as higher-degree students, within the program",
      "Provide input as a member of the Institute Executive Management Committee on Institute priorities, and advocate for my research program",
      "Developed and implemented new project management processes, including making agile management strategies standard practice."
    ),
    "Deputy Program Leader", "2017", "2021",
    "Institute for Positive Psychology and Education, Australian Catholic University",
    list(
      "Supported Program Leader to manage the research program"
    ),
    "Research Fellow", "2016", "Current",
    "Institute for Positive Psychology and Education, Australian Catholic University",
    list(
      "Conduct original, high-impact, and translational research in the areas of health, education, and psychology.",
      "Oversee the development, evaluation, and management of multiple large-scale school-based research projects (e.g., iPLAY; 180 schools).",
      "Conduct analyses of primary and secondary data, and provided statistical support to colleagues including statistics workshops.",
      "Work with industry partners (NSW Department of Education, NSW Health, Sport Australia) to provide project updates and seek input.",
      "Author academic and non-academic outputs, including journal articles, grant applications, stakeholder reports, and data visualisations.",
      "Mentor doctoral and honours students, including reviewing and evaluating their analyses and writing."
    )
    # nolint end
  )

detailed_entries(
  employment,
  what = org,
  when = glue("{start}--{end}"),
  with = role,
  why = details
)
```

# Research Summary

```{r}
tribble(
  # nolint start
  ~Publications, ~Citations, ~"h-Index", ~"Mean CNCI", ~"Mean Impact Factor", ~Funding,
  research_profile$pubs, research_profile$cites, research_profile$h_index, research_profile$mean_cnci, research_profile$mean_jif, "> $1 million"
  # nolint end
) %>%
  knitr::kable(format = "latex", align = rep("c", 5)) %>%
  kableExtra::row_spec(0, bold = TRUE) %>%
  kableExtra::kable_minimal(latex_options = "hold_position", full_width = TRUE)
```

# Technical Skills

```{r skills}
tribble(
  ~Category, ~Skill,
  # nolint start
  "Programming Languages", "R, Python, Stata, Julia",
  "Software Development", "R packages (including CRAN submission), Python packages",
  "Statistical Methods", "Machine learning, multilevel modelling, intervention evaluation, meta-analyses",
  "Research Methods", "Study design, intervention development, ethics and recruitment"
  # nolint end
) %>%
  detailed_entries(
    with = Category,
    what = Skill
  )
```

\newpage

`r if (!params$two_page && !params$five_page) {"# Publications"} else {"# Selected Publications"}`

`r if (params$two_page) {"For a full list of publications see my full CV ([bit.ly/TarenSanders](https://bit.ly/TarenSanders))."}`

`r if (params$five_page) {"## Top Five Publications"}`

```{r top-five-publications, eval = params$five_page}
if (params$five_page) {
  peer_reviewed_citations %>%
    dplyr::filter(top_five) %>%
    arrange(desc(issued))
}
```

`r if (params$five_page) {"## Other Peer-Reviewed Publications"} else {"## Peer-Reviewed Publications"}`

`r if (!params$two_page && !params$five_page) {"*Note*: In health and medicine the last author is considered the 'senior' author.\nCitations from Web of Science; JIF = [Journal Impact Factor](http://help.prod-incites.com/inCites2Live/indicatorsGroup/aboutHandbook/usingCitationIndicatorsWisely/jif.html); CNCI = [Category Normalised Citation Index](http://help.prod-incites.com/inCites2Live/indicatorsGroup/aboutHandbook/usingCitationIndicatorsWisely/normalizedCitationImpact.html)."}`

```{r publications}
if (params$two_page) {
  peer_reviewed_citations %>%
    dplyr::filter(short_cv) %>%
    arrange(desc(issued))
}

if (params$five_page) {
  peer_reviewed_citations %>%
    dplyr::filter(!top_five) %>%
    arrange(desc(issued))
}

if (!params$two_page && !params$five_page) {
  peer_reviewed_citations %>%
    arrange(desc(issued))
}
```

## Book Chapters

```{r bookchapters}
book_chapters %>%
  arrange(desc(issued))
```

`r if (params$five_page) {"\\newpage"}`

```{r five-page-sections, child=if(params$five_page || (!params$two_page && !params$five_page)) 'cv/five_page_sections.Rmd'}
```

```{r other-sections, child=if(!params$two_page && !params$five_page) 'cv/other_sections.Rmd'}
```